Theorems and Proofs

### 2017-05-31 Thresholding Bandit/Theorem2.Rmd
Add start of chapter three

--- 
title: "Theorems and Proofs"
author: "Tim Radtke" 
date: "4/23/2017"
header-includes:
   - \usepackage[retainorgcmds]{IEEEtrantools}
keep_tex: TRUE
output:
  pdf_document
---

@@

Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
all arms $\nu_k$ of the problem are R-sub-Gaussian with means $\mu_k$. Let $\tau
\in \mathbb{R}, \epsilon \geq 0$.

@@

where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
$\mathbb{E}$ is the expectation according to the samples of the problem.

### Proof

To prove above theorem, we first define a favorable event $\xi$ on which we hope
to make a loss with only a small probability. Indeed, it is the event for which
we want to upper bound the expected loss. As we want to find an upper bound for
the expected loss of the APT algorithm, the event corresponds to the decision
made by it. The APT algorithm's heuristic leads to a decision with low expected
regret, if it finds empirical mean estimates $\frac{1}{s} \sum_{t=1}^s X_{i,t}$
of the arms that are close to the true mean $mu_i$ of the arms. Then, we would
expect arms which are over $\tau + \epsilon$ to be classified correctly, and
arms that are under $\tau - \epsilon$ to be rejected.

Indeed, we have $\mathbb{E}(\mathcal{L}(T)) = P(S_{\tau + \epsilon} \cap
\hat{S}_\tau^C \neq \emptyset \lor S_{\tau-\epsilon}^C \cap \hat{S}_{\tau} \neq
\emptyset)$. But this just corresponds to $P(\{\exists i: ((\mu_i <
\tau-\epsilon) \land(\hat{\mu}_i \geq \tau)) \lor ((\mu_i > \tau + \epsilon)
\land (\hat{\mu}_i < \tau)))$. Each of the two $(...)\lor(...)$ conditions
corresponds to $| \hat{\mu}_i - \mu_i | \geq \epsilon$. It follows that the
expected loss can be rewritten as: $\mathbb{E}(\mathcal{L}(T)) = P(\exists i,
\exists s: |\hat{\mu}_{i,s} - \mu_i | \geq \epsilon) = P(\xi^C)$. But this is
exactly the probability of classifying at least one arm incorrectly which
results in a loss of size 1.

Thus we define as the favorable event:

@@

Furthermore, if we write $\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon
\}$, then the following holds by union bound.

@@

...

Plugging \eqref{theorem2_hoeffding} back into \eqref{theorem2_prob_fav_event},
we get:
\begin{equation}
P(\xi) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2})
\end{equation}

Now, in order to match the performance of the lower bound on the expected loss derived in theorem 1, we will choose $\epsilon = \sqrt{\frac{T \delta^2}{Hs}}$. Thus:

@@

Thus, we don't exactly get the bound from Locatelli et al. (2016) because we used the Hoeffding inequality instead of the martingale bound; but the the method should be clear.

>>>>

--- 
title: "Theorems and Proofs"
author: "Tim Radtke" 
date: "4/23/2017"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

@@

\begin{theorem}[Locatelli et al., 2016] \label{theorem:LocatelliTheorem4}
Let $K \geq 0$, $T \geq 2K$, and consider a problem $\mathbb{B}$. Assume that
all arms $\nu_k$ of the problem are R-sub-Gaussian with means $\mu_k$. Let $\tau
\in \mathbb{R}, \epsilon \geq 0$.

@@

where we remind that $H = \sum_i (|\mu_i - \tau | + \epsilon)^{-2}$ and where
$\mathbb{E}$ is the expectation according to the samples of the problem.
\end{theorem}

*Proof of Theorem \ref{theorem:LocatelliTheorem4}:* To prove above theorem, we first define a favorable event $\xi$ on which we hope
to make a loss with only a small probability. Indeed, it is the event for which
we want to upper bound the expected loss. As we want to find an upper bound for
the expected loss of the APT algorithm, the event corresponds to the decision
made by it. Given that the APT algorithm's sampling rule and final decision is based on the empirical mean of each arm, it will have low expected regret, if it finds empirical mean estimates $\hat{\mu}_i(t) = \frac{1}{s} \sum_{t=1}^s X_{i,t}$
that are close to the true means $\mu_i$ of the arms. Then, we would
expect arms with $\hat{\mu}_i(T) > \tau + \epsilon$ to be classified correctly, and
arms with $\hat{\mu}_i(T) < \tau - \epsilon$ to be rejected.

Indeed, we have $\mathbb{E}(\mathcal{L}(T)) = P(S_{\tau + \epsilon} \cap
\hat{S}_\tau^C \neq \emptyset \lor S_{\tau-\epsilon}^C \cap \hat{S}_{\tau} \neq
\emptyset)$. But this just corresponds to $P(\{\exists i: ((\mu_i <
\tau-\epsilon) \land(\hat{\mu}_i \geq \tau)) \lor ((\mu_i > \tau + \epsilon)
\land (\hat{\mu}_i < \tau)))$. Each of the two $(...)\lor(...)$ conditions
corresponds to $| \hat{\mu}_i - \mu_i | \geq \epsilon$. It follows that the
expected loss can be rewritten as: $\mathbb{E}(\mathcal{L}(T)) = P(\exists i,
\exists s: |\hat{\mu}_{i,s} - \mu_i | \geq \epsilon) = P(\xi^C)$. This is
exactly the probability of classifying at least one arm incorrectly which
results in a loss of size 1.

Thus we define as the favorable event as:

@@

Furthermore, if we write $\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon
\}$, then the following holds by a union bound.

@@

\begin{lemma}[Hoeffding's Inequality] \label{lemma:HoeffdingInequality}
Consider $X_1, \dots, X_T$ independent random variables from R-sub-Gaussian distributions $\nu_i$ with mean $\mu_i$. Then, for any $\epsilon > 0$,

\begin{equation*}
\mathbb{P} \Big( | \sum_{i = 1}^T (X_i - \mu_i) | \geq \epsilon \Big) \leq 2\exp \Big(\frac{-\epsilon^2}{2T R^2}\Big).
\end{equation*}
\end{lemma}

Plugging equation \eqref{theorem2_hoeffding} back into equation \eqref{theorem2_prob_fav_event},
we get:
\begin{equation}
P(\xi) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) \geq 1 - 2 \sum_i \sum_s \exp (-\frac{\epsilon^2 s}{2 R^2})
\end{equation}

Now, in order to match the performance of the lower bound on the expected loss derived in Theorem \ref{theorem:Locatelli2016Theorem1}, we will choose $\epsilon = \sqrt{\frac{T \delta^2}{Hs}}$. Thus:

@@

Thus, we do not exactly get the bound from Locatelli et al. (2016) because we used the Hoeffding inequality instead of the martingale bound; but the the method should be clear.
